Value-Suppressing Uncertainty Maps

### 2017-12-11 paper/main.tex
Fix small typos

We selected this task both as a way of assessing the ability of people to successfully encode and decode values using a bivariate map, and to provide training for the prediction task (since we re-used the bivariate maps in that task). We measured performance both in terms of accuracy (did the participant select the correct point) as well as response time.

@@

We selected this task in order to promote risk-averse behavior. Tversky \& Kahneman~\cite{tversky1985framing} illustrate that framings in terms of gains or losses produce reliably different outcomes. In particular, there is greater perceived value in avoiding large losses as opposed to striving for a large gain~\cite{kahneman1979prospect}. Our results from the prior study indicate that discrete, non-juxtaposed maps outperformed the other bivariate maps we selected, so we limited our study to only 4 types: square and wedge bivariate maps. While other map types might produce different patterns of decision-making (for instance, the juxtaposed map might encourage participants to ignore uncertainty information altogether), their low accuracy for our previous information fusion tasks led us to discard them, as it would be difficult to distinguish between different patterns of predictions caused by the design, and different patterns caused by simply misreading the heatmap. Having fewer conditions also afforded a within-subjects design that controlled for the variation in inter-personal differences in strategies and risk-aversion, while limiting the potential effects of learning and fatigue on predictions from large numbers of stimuli.

@@

The results support our second hypothesis. A similiar ANOVA for average danger value of guesses found a significant effect of quantization scheme ($F(1,59)=17$, $p<0.01$). A post-hoc t-test confirmed ($t=2.3$, $p=0.02$) that guesses made with VSUPs had significantly higher average danger ($M=0.32$, $SD=0.17$) (and so lower expected value) than traditional maps ($M=0.29$, $SD=0.18$).

>>>>

We selected this task both as a way of assessing the ability of people to successfully encode and decode values using a bivariate map, and to provide training for the prediction task (since we reused the bivariate maps in that task). We measured performance both in terms of accuracy (did the participant select the correct point) as well as response time.

@@

We selected this task in order to promote risk-averse behavior. Tversky \& Kahneman~\cite{tversky1985framing} illustrate that framings in terms of gains or losses produce reliably different outcomes. In particular, there is greater perceived value in avoiding large losses as opposed to striving for a large gain~\cite{kahneman1979prospect}. Our results from the prior study indicate that discrete, non-juxtaposed maps outperformed the other bivariate maps we selected, so we limited our study to only 4 types: square and wedge bivariate maps. While other map types might produce different patterns of decision-making (for instance, the juxtaposed map might encourage participants to ignore uncertainty information altogether), their low accuracy for our previous information fusion tasks led us to discard them, as it would be difficult to distinguish between different patterns of predictions caused by the design, and different patterns caused by simply misreading the heatmap. Having fewer conditions also afforded a within-subjects design that controlled for the variation in interpersonal differences in strategies and risk-aversion, while limiting the potential effects of learning and fatigue on predictions from large numbers of stimuli.

@@

The results support our second hypothesis. A similar ANOVA for average danger value of guesses found a significant effect of quantization scheme ($F(1,59)=17$, $p<0.01$). A post-hoc t-test confirmed ($t=2.3$, $p=0.02$) that guesses made with VSUPs had significantly higher average danger ($M=0.32$, $SD=0.17$) (and so lower expected value) than traditional maps ($M=0.29$, $SD=0.18$).
